Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-03-03 paper/1_Initial/manuscript.qmd
@AnafNeves added todo in data analysis

Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., on all samples separately) to add nuance to the general picture, as all studies differ in their sample sizes, demographics, language, and procedure.

@@

@@

#### Statistical Analysis

To examine the factor structure of the IAS, a two-steps approach was employed.
First, EGA  was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
Subsequently, exploratory factor analysis (EFA) was employed followed by CFA.

@@

<!-- Distibutions of items -->

@@

<!-- Note: this table is generated during data analysis -->
\input{../../analysis/figures/table2.tex}

>>>>

Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., on all samples separately) to add nuance to the general picture, as all studies differ in their sample size, demographic characteristics, language, and procedure.

@@

<!-- Note: this table is generated during data analysis -->

@@

In order to obtain a comprehensive view, we will examine the factor structure of the IAS using two different approaches, namely Exploratory Graph Analysis (EGA) and traditional exploratory and confirmatory Factor Analysis (EFA/CFA).

**TODO: Explain EGA. Rework the following paraphraph**.

<!-- was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory]. -->
<!-- The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates. -->
<!-- A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25). -->

In contrast, the factor analsyis framework... **TODO**. 
We will first apply EFA to... and then identify the best fitting models using CFA.

@@

<!-- Distributions of items -->

@@

\input{../../analysis/figures/table2.tex}
